Open Data, Open Source and Open Standards in chemistry - The Blue Obelisk five years on

### 2011-05-13 paper.tex
Tidy up comp chem section

>>>>

\subsection*{Computational chemistry analysis}

Another area where the Blue Obelisk has had a signficant impact in the
past five years is in supporting
quantum chemistry calculations and in interpreting their results.
Electronic structure calculations have a long tradition in the
chemistry community and a variety of programs exist, mostly
proprietary software with the notable exception of NWChem.
However, since each program uses different input formats, and the
results are output differently even varying between different versions
of the software, preparing calculations and extracting the results in
an automated way is problematic.

Avogadro has already been mentioned as a GUI for preparing
computational chemistry calculations. It uses Open Babel to read the
output of several electronic structure packages, and also to write the
input files for each. Jmol (see below) can also depict computational
chemistry results including molecular orbitals.

In 2006, the Blue Obelisk project cclib~\cite{cclib} was established
with the goal of parsing the output from computational chemistry
programs and presenting it in a standard way so that further analyses
could be carried out independently of the quantum package used to
obtain the results. cclib is a Python library, and
the current version (version 1.0.1)
supports 8 different computational chemistry codes and extracts over
30 different calculated attributes. A related BO project,
GaussSum~\cite{WebGaussSum},
is a GUI that builds on top of cclib to allow predicted properties to
be compared to experimental properties (for example, the calculated
vibrational frequencies and the IR spectrum).

[Few lines on Quixote here]
